PWNCAT2

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_introduction.tex
update

In this section, we will search for emission in the phase range between
the peaks of the pulsar's light curve. This potential DC emission could originate
in the pulsar's winds, from inside the pulsar's magnetosphere, or 
the emission could be spatially coincidental but physically
unrealted to the pulsar.

The \gev emission in the off-peak from LAT-detected pulsars has been studied in several previous 
publications. In particular, the spatially-extended \velax pulsar wind nebula has
been detected by the LAT in the off-peak phase region of the Vela pulsar \citep{LAT_collaboration_Vela_X_2010}
and the Crab nebula has been detected by the LAT \citep{LAT_collaboration_crab_2010}.
Surprisingly, this \gev emission from the Crab nebula was found to be variable
in time \citep{LAT_Collaboration_Crab_Flare_2011}.

Most prominently, a dedicated analysis was performed using LAT data of
the off-peak emission of 54 LAT-detected pulsars using 16 months of survey observations
\citep{LAT_collaboration_PWNCAT_2011}. 
The search discovered ten pulsars wich significant off-peak emission.
Along with \velax and the Crab nebula, the 
search discovered a source coincident with the TeV source HESS\;J1023-575
in the off-peak window of PSR\;J1023-5746. In addtion, four of hte other
regions showed a significantly cutoff pulsar-like spectrum and are
suspected to be be of magnetospheric origin.

We expand upon this previous work by searching in the off-peak region
of all 107 pulsars presented in this catalog. In addition to the larger
list of pulsars, in this earch we use an expanded data set, a larger energy range,
and an improved analysis method.

>>>>

In this section, we will search for emission in the phase range between
the peaks of the pulsar's light curve. This potential DC emission could originate
in the pulsar winds, from inside a pulsar's magnetosphere, or 
the emission could be physically unrealted to the pulsar.

\gev emission in the off-peak regions around LAT-detected
pulsars has been studied in several previous publications. In
particular, the spatially-extended \velax pulsar wind nebula has
been detected by the LAT in the off-peak region of the Vela pulsar
\citep{LAT_collaboration_Vela_X_2010} and the Crab nebula has been
detected by the LAT \citep{LAT_collaboration_crab_2010}.  Surprisingly,
this \gev emission from the Crab nebula was found to be variable in
time \citep{LAT_Collaboration_Crab_Flare_2011}.

Most prominently, a dedicated analysis was performed using LAT data of
the off-peak emission of 54 LAT-detected pulsars using 16 months of survey
observations \citep{LAT_collaboration_PWNCAT_2011}.  The search discovered
ten pulsars with significant off-peak emission.  Along with \velax and the
Crab nebula, the search discovered a source coincident with the TeV source
HESS\;J1023-575 in the off-peak window of PSR\;J1023-5746. In addtion,
four of the other regions showed a significantly cutoff pulsar-like
spectrum and are suspected to be of magnetospheric origin.

We expand upon this previous work by searching in the off-peak region
of all 117 pulsars in this catalog. In addition to the larger list of
pulsars, we use an expanded observation time, a larger energy range,
and an improved analysis method.

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_results.tex
update

First, we tested the sources to see if they
were spatially extended. The localization results are in \tabref{offpeak}.

@@

Next, we performed a spectral analysis over all energy using the best
fit morphology. XXX shows the results of the all energy
analysis of the off-peak emission for each pulsar.

Next, we fit a powerlaw independently in each energy
bin. XXX shows the results of the analysis in separate
energy bins of each pulsar.

Finally, we tested sources to see which were
variable. XXX shows the results of the cutoff test for
pulsars with significant low-energy emission.

@@

We tested all sources for variability.

Special cases:
\begin{itemize}
  \item Crab has a funny spectrum, we have (so far) fixed it to
  \item \velax
\end{itemize}

>>>>

After analyzing the off-peak emission using the pipeline described
in \subsecref{off_peak_analysis}, we consider any emission in the
off-peak region to be magnetospheric in nature if the emsision is
not significantly-extended and has a significantly-cutoff spectrum.
We consider the emission to originate in the pulsar wind if it is
spatially extended or had a hard spectral index.
If the source is point-like and had a soft spectrum, or if it 
is spatially extended but the extension is biased by modeling
of the background, we are unable to determine the origin of the emission.

A summay of the reuslts of the pipepline can be found in \tabref{offpeak}.
It includes off off-peak phase ranges selected using the method described
in \subsecref{off_peak_defintion}.
This table includes \ts, \tsext, and \tscut
for the significantly detected pulsars (with $\ts>25$).
This table also includes the best fit flux and spectral index for these pulsars assuming
the best hypothesis (either point-like, spatially-extended, or expontentially cutoff).
For the sources that are significantly cutoff, the spectral index refers to the index
from the fit of a cutoff spectral model and the final column includes the cutoff energy derived from the fit.

@@

@@

Consistent with \citep{LAT_Collaboration_Crab_Flare_2011}, we found
the Crab nebula to be highly variable with \tsvar=XXXX.  Besides that,
we found no significantly variable off-peak emission.  The results of
the variability test are contained in the auxiliary information.

The results of the spectral analysis in smaller energy bands described
in section \secref{peak_analysis} are included in the auxiliary
information. In addition, upper limits computed assuming a powerlaw
spectral model and a canonical pulsar spectrum are included in the
auxiliary information.

Results:
\begin{itemize}
  \item List of all XXX detections
  \item For each pulsar, is it a 
    \begin{itemize}
      \item Magnetospheric emission
      \item PWN emission
      \item Region where the fit shows trouble for some reason.
    \end{itemize}
\end{itemize}

In our analysis, we detected the the Vela X PWN (associated with PSRJ0835$-$4510), the Crab Nebula (associated
with PSRJ0534+2200), and MSH 15$-$52 (associated with PSRJ1513-5908).

What to say about PSRJ1023-5746

Sources we detect as clearly magnetospheric

Special cases/problem cases:
\begin{itemize}
  \item PSRJ0101-6422: Very weird spectrum
  \item PSRJ1112-6103: Very close to MSH 11~62 (arXiv:1202.3371v1). Nearby source is 2FGL J1112.1-6040. Significant extension.
  \item When fitting PSRJ1119-6127, description of adding nearby point
  source to represent emission residual from o represent residual from
  PSRJ1112-6103 looking spatially
    extended.
  \item PSRJ1418-6058 and PSRJ1420-6048, very difficult to analyze because both very near eachother.
  \item Something about the complciated Gamma Cygni PSR: PSRJ2021+4026
  \item PSRJ1105-6107: something about adding source to background model that is very nearby. \todo{See what OZLEM is doing}.
  \item PSRJ1648-4611 (what to do about nearby 2FGL soruce and other residual emission. Is this paper relevant: http://arxiv.org/pdf/1111.2043.pdf???)?
  \item What to do about emission from PSR J1023 at low energy???
  \item PSRJ0908-4913: waht to say about far localization?
\end{itemize}

\todo[inline]{Describe how we present the point-like hypothesis for signifciant extended soures if the extension fails for some reason}
